INTELLIGENT SYSTEMS

### 2021-04-02 paper_4.tex
finish 4.3.5

\subsubsection{Cameras}
Three types of camera are used for the construction of the dataset. Two 
of these belong to the high-end, while a third belongs to the category of 
mobile phones. To achieve correct color correction, several 3x3 size color 
conversion matrices (\emph{CCMs}) were used. In other words, try to transform 
the components of the image from RGB to sRGB in order to adapt them to 
the lighting under which the image is viewed. For the outdoors, 10 CCMs 
were used based on the type of illumination. Another factor that required 
correction was the color shading (\emph{CS}). This only requires correction for the 
images coming from the mobile phone.

>>>>

\subsubsection{Cameras}
Three types of camera are used for the construction of the dataset. Two 
of these belong to the high-end, while a third belongs to the category of 
mobile. To achieve correct color correction, several 3x3 size color 
conversion matrices (\emph{CCMs}) were used. In other words, try to transform 
the components of the image from RGB to sRGB in order to adapt them to 
the lighting under which the image is viewed. For the outdoors, 10 CCMs 
were used based on the type of illumination. Another factor that required 
correction was the color shading (\emph{CS}). This only requires correction for the 
images coming from the mobile.

\subsubsection{Scene Contents}
The scenes that make up the dataset are divided into lab scenes and field 
scenes. There are several types of different lab scenes, each having 5 different 
illuminations (Fig. \ref{fig:Lab}). Both the lab scenes and those acquired in the field 
are 64, for a total of 128 scenes. Each lab scene is captured with each camera 
in almost the same shot. An attempt was made to preserve the same settings 
in the field scenes even if the latter have different lighting. In order to have 
good stabilization, a fixed tripod is used.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.6 \linewidth]{images/paper4/lab.png}
    \centering
    \caption{Lab real scenes}
    \label{fig:Lab}
\end{figure}

\subsubsection{Ground Truths}
The ground-truth is based on the chromaticity of the illumination, or white 
points, assumed by the camera which can change for each image. This parameter 
is calculated by averaging the achromatic colors present in the lighter 
patches of the color-checker, that appear in the last line.

\subsubsection{Recommendations for Evaluating CC Algorithm Performance}
In order to evaluate the performance of the algorithm with this type of 
dataset, it is recommended to use the following strategies:
\begin{enumerate}
    \item \emph{Camera independence}: the article proposes six-fold cross validation, 
    where each fold, divided into training, validation and test, contains a 
    grouping of images for each of the nine cameras. This technique aims 
    to obtain a fair evaluation of camera-independence of an algorithm (the 
    algorithm considers all images as if coming from the same camera).
    \item \emph{Camera and Scene Independence}: in this case it is recommended to 
    use the images acquired by Nikon and the mobile for training, while 
    the Canon images must be used for validation. As for the test, it is 
    recommended to use the Canon images belonging to the second group 
    of images. In this way you can understand the influence of camera-
    independence. If you get a low error, which means that the algorithm 
    treats each scene (each made up of images captured by different cameras) 
    as if it had been captured entirely by a single camera, then at 
    this point you would get, in addition to independence of the camera, 
    the independence of the scene. This is a good result if it is achieved in 
    this type of dataset.
    \item \emph{Camera and Scene Independence from Single Camera}: in this strategy 
    it is suggested to use the images from the second group as training 
    and validation while using the images acquired by Nikon and the 
    mobile for testing. In this way we want to understand if the algorithm 
    obtains the camera/scene independence effect with images produced 
    by another different camera (Canon). If this technique were 
    used with the 1 (where a low error implies the achievement of the 
    camera-independence) then when new images of different origin would 
    be inserted, the error would be higher than that obtained in 1, this is 
    because the camera-independence it faces the old set of cameras and not 
    the new one. It is being said that thanks to the combination of these, 
    it is possible to have a targeted camera-independence and a targeted 
    scene-independence for each new camera.
    \item \emph{Testing the Effect of Color Shading}: if you were to use the images 
    of your mobile, to test their color shading correction (CS), you could 
    enclose them all in a test set. Images that cause a high error will be 
    those that have not undergone the correction process.
    \item \emph{Testing the Effect of Resolution}: color constancy can be easily calculated when the images are at high resolution. As you can guess, this result is not achievable with images from a mobile phone. For this reason, the dataset contains a portion of image downscaling (1080p) useful for observing how the resolution can affect the performance of the algorithm.
\end{enumerate}
